%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classic Professional Resume
% LaTeX Template
%
% This template uses standard LaTeX classes and packages for a clean,
% recruiter-friendly single-column layout.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% Clean style for section headings with dividing lines
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Clean bullet lists with minimal padding
\setlist[itemize]{leftmargin=1.5em, noitemsep, topsep=2pt}

% Configure hyperlink coloring
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\begin{document}
\pagestyle{empty}

% Contact Information Header
\begin{center}
    {\LARGE \bfseries Richard Louie Orilla} \\
    \vspace{4pt}
    Davao City, Philippines \ $\bullet$ \ \href{mailto:richardorilla@pm.me}{richardorilla@pm.me} \ $\bullet$ \ \href{http://www.richardorilla.website}{www.richardorilla.website} \\
    \href{https://github.com/Shin-Aska}{github.com/Shin-Aska} \ $\bullet$ \ \href{https://mastodon.social/@richardorilla}{mastodon.social/@richardorilla} \ $\bullet$ \ \href{https://pixelfed.social/richard\_orilla}{pixelfed.social/richard\_orilla}
\end{center}

\vspace{6pt}

% Education Section
\section{Education}
\noindent
\textbf{De La Salle University} \hfill 2017--2019 \\
M.Sc. in Computer Science (Coursework Completed) \\
\vspace{4pt}
\noindent
\textbf{University of Mindanao} \hfill 2010--2015 \\
B.Sc. in Computer Science (Status: Graduated)

% Experience Section
\section{Experience}

\noindent
\textbf{inRiver} \hfill Present \\
\textit{Technical Lead}
\begin{itemize}
    \item Architected 5 interconnected microservices (CMS, Central Command, Spider, ETL, Post-Processing) using Python and Azure DevOps CI/CD to manage enterprise-scale web scraping workflows with isolated, per-customer databases.
    \item Led a team of 8 engineers in designing the complete data pipeline and designed SQL Server schemas for customer data synchronization via CMS with real-time replica databases, ensuring zero cross-customer data leakage.
    \item Evolved the architecture into an AI Agent Orchestrator using Python, and engineered an interactive client-side AI Chat UI using React that manages session state purely in-browser to comply with strict EU data privacy laws.
    \item Spearheaded the design of a C\# data mapper to interface the core C\# PIM platform with Python services, facilitating seamless post-acquisition corporate technology integration.
    \item Coded Vue + Quasar front-ends and managed the transition to modern React applications designed with Material UI (MUI).
    \item Standardized containerized infrastructure using Docker and Kubernetes (Helm) to reduce deployment friction across staging and production environments.
\end{itemize}

\vspace{8pt}

\noindent
\textbf{Detail Online} \hfill 2018--2022 \\
\textit{Senior Backend Developer}
\begin{itemize}
    \item Maintained high-performing NodeJS and JavaScript backend applications to process compliance results, building custom query engines that enabled efficient dynamic client-side sorting and row-fetching.
    \item Engineered a portable C\#/.NET Windows desktop application to automate and streamline data validation QA workflows for internal teams.
    \item Built ML-powered automation tools in Python using TensorFlow, Caffe, and Darknet to eliminate manual data processing, saving 8 hours of labor overhead per week.
    \item Designed and delivered 15+ production REST APIs in Python interacting with PostgreSQL databases to service organization-wide data pipeline integrations.
    \item Conducted technical evaluations of third-party AI platforms and prototyped vision-based ML models in PyTorch to benchmark capabilities against requirements, saving an estimated \$50K in licensing costs.
\end{itemize}

\vspace{8pt}

\noindent
\textbf{University of Mindanao} \hfill 2015--2018 \\
\textit{Computer Science Instructor}
\begin{itemize}
    \item Instructed academic coursework covering Fundamentals of Programming, Object-Oriented Programming (OOP), Database Programming (SQL Server/IBM DB2 fundamentals), Visual Programming, Game Development, and Security.
    \item Developed curricula, prepared lectures, and mentored over 100+ undergraduate students in software engineering and database design concepts.
\end{itemize}

\vspace{8pt}

\noindent
\textbf{Freelance Software Developer} \hfill 2015--2018 \\
\textit{Independent Contractor}
\begin{itemize}
    \item Maintained legacy business-critical C++ desktop applications integrated with MySQL, resolving bugs and implementing minor feature updates (2016--2017).
    \item Developed custom WordPress PHP plugins and maintained Laravel e-commerce web applications to support client online scaling and feature updates.
\end{itemize}

% Technical Skills Section
\section{Technical Skills}
\noindent
\textbf{Languages:} Python, C\#, TypeScript, JavaScript, SQL, C++, PHP, HTML, CSS \\
\textbf{Frameworks \& Libraries:} React, Vue, NodeJS, Quasar, Material UI (MUI), Laravel, TensorFlow, PyTorch \\
\textbf{Tools \& Database:} Docker, Kubernetes, Helm, Git, Azure DevOps, SQL Server, PostgreSQL, MySQL, IBM DB2, \LaTeX

% Projects & Research Section
\section{Projects \& Research}
\noindent
\href{https://github.com/Shin-Aska/DosboxStagingReplacerForGOGGalaxy}{\textbf{DOSBox Staging Replacer}} \hfill \textit{C++} \\
Open-source utility that replaces GOG Galaxy's default DOSBox emulator, resolving scaling and performance issues for retro gaming on modern platforms.

\vspace{4pt}
\noindent
\href{https://github.com/Shin-Aska/amagon-html-editor}{\textbf{Amagon HTML Editor}} \hfill \textit{TypeScript, React, Electron, GitHub Actions, AI} \\
Offline visual editor featuring bidirectional code/canvas sync, natural language page building, and automated cross-platform releases via GitHub Actions CI/CD.

\vspace{4pt}
\noindent
\href{https://github.com/Shin-Aska/team-report-generator}{\textbf{Team Report Generator}} \hfill \textit{Laravel, Gemini AI} \\
LLM-driven daily update summarizer with secure JSON proxy, CORS, and rate limiting.

\vspace{4pt}
\noindent
\href{https://github.com/Shin-Aska/s2sc.js}{\textbf{s2sc.js Transpiler}} \hfill \textit{Compiler Construction} \\
Source-to-source compiler exploring language interoperability via AST parsing and code generation.

\vspace{4pt}
\noindent
\href{https://github.com/Shin-Aska/poc-camera-ml}{\textbf{Hand Tracking Game}} \hfill \textit{Computer Vision, 3D Physics} \\
Browser-based game using MediaPipe landmark detection mapped to React Three Fiber + Rapier.

\end{document}
